---
title: "figure_arrangement"
author: "Christian Holland"
date: "22/01/2019"
output: html_document
---
```{r "knitr config", cache=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::knit(..., quiet = TRUE)
```


```{r "setup", message=F}
library(tidyverse)
library(cowplot)
library(magick)
```
## Arranging indiviual figures into a grid/collage
### Main figures
#### Figure 1 - Benchmark overview
```{r "Figure 1"}
fig1_1 = plot_grid(
  ggdraw() + draw_image("paper/figures/sub/Figure1a.png"),
  ggdraw() + draw_image("paper/figures/sub/Figure1c.png"),
  labels=c("A", "C"), label_size = 18
)

fig1 = plot_grid(
  fig1_1,
  ggdraw() + draw_image("paper/figures/sub/Figure1b.png"),
  ncol=1, labels=c("", "B"), label_size = 18
  )
ggsave("paper/figures/Figure1.png", fig1, width=10, height=10)

```
#### Figure 2 - PROGENy benchmark results
```{r "Figure 2"}
global_roc_curve = readRDS("fig/progeny_benchmark/global_roc_curve.rds")
global_pr_curve = readRDS("fig/progeny_benchmark/global_pr_curve.rds")

fig2 = plot_grid(global_roc_curve, global_pr_curve, 
                 labels = c("A", "B"), label_size = 18)
ggsave("paper/figures/Figure2.png", fig2, width = 10, height=5)
```

#### Figure 3 - DoRothEA benchmark results
```{r "Figure 3"}
auroc_vs_conf = readRDS("fig/dorothea_benchmark/auroc_vs_conf.rds")
auprc_vs_conf = readRDS("fig/dorothea_benchmark/auprc_vs_conf.rds")
global_roc_curve = readRDS("fig/dorothea_benchmark/global_roc_curve.rds")
global_pr_curve = readRDS("fig/dorothea_benchmark/global_pr_curve.rds")

fig3 = plot_grid(auroc_vs_conf, auprc_vs_conf, 
                 global_roc_curve, global_pr_curve, 
                 labels = c("A", "B", "C", "D"), label_size = 18,
                 align="v")
ggsave("paper/figures/Figure3.png", fig3, width = 10, height=10)
```

#### Figure 4 - Disease enrichment
```{r "Figure 4"}
volcano_plot_pw = readRDS("fig/disease_enrichment/volcano_plot_pw.rds")
volcano_plot_tf = readRDS("fig/disease_enrichment/volcano_plot_tf.rds")

fig4_1 = plot_grid(ggdraw() + draw_image("paper/figures/sub/Figure4a.png"),
                   labels = "A", label_size=18)

fig4_2 = plot_grid(
  volcano_plot_pw, 
  volcano_plot_tf, 
  ncol=1, labels=c("B", "C", ""), label_size=18, align="v", axis="l")

fig4 = plot_grid(fig4_1, fig4_2, ncol=2)
ggsave("paper/figures/Figure4.png", fig4, width=10, height=10)
```
### Supplement figures
#### Figure S1 - PROGENy pathway-wise benchmark results using ROC
```{r "Figure S1"}
pw_roc_curve = readRDS("fig/progeny_benchmark/pw_roc_curve.rds")
figS1 = pw_roc_curve
ggsave("paper/figures/FigureS1.png", figS1, width = 10, height=10)
```

#### Figure S2 - PROGENy benchmark downsampled
```{r "Figure S2"}
global_tp_tn_ratio = readRDS("fig/progeny_benchmark/global_tp_tn_ratio.rds")
auroc_downsampled = readRDS("fig/progeny_benchmark/auroc_downsampled.rds")

figS2 = plot_grid(global_tp_tn_ratio, auroc_downsampled, labels = c("A", "B"),
                  label_size = 18)
ggsave("paper/figures/FigureS2.png", figS2, width = 10, height=5)
```

#### Figure S3 - PROGENy pathway-wise benchmark results using PR
```{r "Figure S3"}
pw_pr_curve = readRDS("fig/progeny_benchmark/pw_pr_curve.rds")
figS3 = pr_curve_pw
ggsave("paper/figures/FigureS3.png", figS3, width = 10, height=10)
```

#### Figure S4 - DoRothEA properties + benchmark downsampled
```{r "Figure S4"}
regulon_properties = readRDS("fig/dorothea_benchmark/regulon_properties.rds")
tf_coverage = readRDS("fig/dorothea_benchmark/tf_coverage.rds")
global_tp_tn_ratio = readRDS("fig/dorothea_benchmark/global_tp_tn_ratio.rds")
auroc_downsampled = readRDS("fig/dorothea_benchmark/auroc_downsampled.rds")

aligned_plots = align_plots(regulon_properties, global_tp_tn_ratio, 
                            align="v", axis="l")

figS4_1 = plot_grid(aligned_plots[[1]], tf_coverage, labels = c("A", "B"), 
                    label_size=18, rel_widths = c(2,1), align="h", axis="bt")
figS4_2 = plot_grid(aligned_plots[[2]], auroc_downsampled, 
                    labels = c("C", "D"), label_size=18,
                    rel_widths = c(1,1), align="h", axis="bt")
figS4 = plot_grid(figS4_1, figS4_2, ncol=1)
ggsave("paper/figures/FigureS4.png", figS4, width = 10, height=10)
```

#### Figure S5 - Comparison between DoRothEA and TRRUST
```{r "Figure S5"}
overlap_dorothea_trrust = readRDS("fig/dorothea_benchmark/overlap_dorothea_trrust.rds")
regulon_similarity = readRDS("fig/dorothea_benchmark/regulon_similarity.rds")
figS5 = plot_grid(overlap_dorothea_trrust, regulon_similarity, 
                  labels = c("A", "B"), label_size = 18)
ggsave("paper/figures/FigureS5.png", figS5, width=10, height=5)
```
